The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-12 paper/ms.tex
Fig7. albedo corrected

\begin{table}
\begin{center}
\begin{tabular}{c c}
\hline \hline
Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
\hline \hline
Homogeneous $10^{5}$& $0.2637, 0.2661, 0.3091, 0.3570, 0.3709$ \\
Homogeneous $10^{6}$ & $0.2894, 0.2891, 0.3096, 0.3607, 0.3937$ \\
Homogeneous $10^{7}$ &$ 0.2279, 0.2298, 0.2318, 0.2547, 0.2813 $\\
Central $10^{5}$ & $0.0966, 0.0966, 0.0965, 0.0965, 0.0965$ \\
Central $10^{6}$ & $0.0663, 0.665, 0.0665, 0.0665, 0.665$ \\
Central $10^{7}$ & $0.0149, 0.0158, 0.0158, 0.0158, 0.0158$ \\
\hline
\end{tabular}
\caption{
 Escape fraction values for all of the models. } 
\label{table:escape}
\end{center}
\end{table}

\begin{figure*}
\begin{center}
  \includegraphics[scale=0.35]{f6.eps}
  \includegraphics[scale=0.35]{f7.eps}
\end{center}
  \caption{Effects of rotaation on the escape fraction. Left
    panel. Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models. Right panel. Escape
    fraction as a    function of the product $(a\tau_{\rm
      H})^{1/3}\tau_{a}$. The    analytic solution for the infinite
    slab is shown as a continuous    line. Different lines correspond
    to different rotational    velocities.     \label{fig:efvsv}} 
\end{figure*}

@@

In Figure \ref{fig:efvsNeufeld} we put these results in the context of
the analytic solution for the infinite slab \citep{Neufeld90}. In
Neufeld's set-up the analytic solution depends uniquely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
\ref{fig:efvsNeufeld} show the results for the different rotational
velocities. First of all we note that the escape fraction does not
increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
that is explained since there is a transition from a opaque to an extremely opaque medium
which affect affects how \ly photons escape from the medium: single flight 
vs. single excursion. {\bf Que quiere decir eso de single flight y
  single excursion, porque explica eso la fraccion de escape?} 
 %we are in a regime where the condition for the analytic expectations
 %($a\tau_{h}\gg 1$) does not hold.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{c c}
\hline \hline
Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
\hline \hline
Homogeneous $10^{5}$& $\ 0.2637\  0.2661\  0.3091\  0.3570\  0.3709$ \\
Homogeneous $10^{6}$ & $\ 0.2894\  0.2891\  0.3096\  0.3607\  0.3937$ \\
Homogeneous $10^{7}$ &$\ 0.2279\  0.2298\  0.2318\  0.2547\  0.2813 $\\
Central $10^{5}$ & $\ 0.0966\  0.0966\  0.0965\  0.0965\  0.0965$ \\
Central $10^{6}$ & $\ 0.0663\  0.0665\  0.0665\  0.0665\  0.0665$ \\
Central $10^{7}$ & $\ 0.0149\  0.0158\  0.0158\  0.0158\  0.0158$ \\
\hline
\end{tabular}
\caption{
 Escape fraction values for all of the models. } 
\label{table:escape}
\end{center}
\end{table}

\begin{figure*}
\begin{center}
  \includegraphics[scale=0.35]{f6.eps}
  \includegraphics[scale=0.35]{f7.eps}
\end{center}
  \caption{Effects of rotation on the escape fraction. Left
    panel. Escape fraction as a function of rotational velocity. All
    these models have $\tau_{a}=1$. The continuous (dashed) lines
    correspond to central (homogeneous) models. Right panel. Escape
    fraction as a    function of the product $(a\tau_{\rm
      H})^{1/3}\tau_{a}$. The    analytic solution for the infinite
    slab is shown as a continuous    line. Different lines correspond
    to different rotational    velocities.     \label{fig:efvsv}} 
\end{figure*}

@@

In the right pnael of Figure \ref{fig:efvsv} we put these results in the context of
the analytic solution for the infinite slab \citep{Neufeld90}. In
Neufeld's set-up the analytic solution depends uniquely on the product
$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in the right panel of Figure
\ref{fig:efvsv} show the results for the different rotational
velocities. First of all we note that the escape fraction does not
increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
that is explained since there is a transition from a opaque to an extremely opaque medium
which affect affects how \ly photons escape from the medium: single flight 
vs. single excursion. {\bf Que quiere decir eso de single flight y
  single excursion, porque explica eso la fraccion de escape?} 
 %we are in a regime where the condition for the analytic expectations
 %($a\tau_{h}\gg 1$) does not hold.
